### 2015-12-16 outline.tex
reorganize outline for preliminary direction of project

\vskip.3in
Main idea: extend SOP$\_$repeated model to endogenize length of dispute
\begin{itemize}
	\item Adapt SOP$\_$repeated (or SOP)
		\begin{itemize}
			\item Note: Chad wonders if repeated game / self-enforcement constraint is essential to story
		\end{itemize}
	\item When is it worth it for lobby to exert effort to prolong trade war?
	\item Chad and Maurizio Zanardi are working on a paper on AD 5-year reviews
		\begin{itemize}
			\item After five years, they come up for review 
				\begin{itemize}
					\item Some AD measures get removed, some not, some go to dispute
					\item This is, of course, conditional on getting to five years
				\end{itemize}
			\item 40 percent of all WTO disputes have to do with AD, but of course not all AD measure go to dispute
			\item They have the data, but are not exploiting cross-industry variation
				\begin{itemize}
					\item Instead, aggregate variation, things like recessions, exchange rates
				\end{itemize}
			\item They don't have a theory for the cross-industry variation, because the economic determinants are meaningless after five years
				\begin{itemize}
					\item No injury, import surges: they've been protected for five years. No variation in new economic date b/c they've been insulated
					\item What's the economic test? There really isn't one. ``Would there be injury if we removed the duty?''
					\item Politics could be that theory (my theory from above)
						\begin{itemize}
							\item Q: Does hiring of lawyers for AD procedure get caught up in LDA data?
						\end{itemize}
				\end{itemize}
		\end{itemize}
\end{itemize}

>>>>

\vskip.3in
Main idea: adapt SOP model to predict whether anti-dumping measures get renewed
\begin{itemize}
	\item Note that this is not trade war (as far as I know: check with Chad): foreign is applying $\tau^{*a}$ in most / all cases
		\begin{itemize}
			\item When is it worth it for lobby to exert effort to renew AD measure?
		\end{itemize}
\end{itemize}

\newpage
\begin{itemize}
	\item Chad and Maurizio Zanardi are working on a paper on AD 5-year reviews
		\begin{itemize}
			\item After five years, they come up for review 
				\begin{itemize}
					\item Some AD measures get removed, some not, some go to dispute
					\item This is, of course, conditional on getting to five years
				\end{itemize}
			\item They have the data, but are not exploiting cross-industry variation
				\begin{itemize}
					\item Instead, aggregate variation, things like recessions, exchange rates
				\end{itemize}
			\item They don't have a theory for the cross-industry variation, because the economic determinants are meaningless after five years
				\begin{itemize}
					\item No injury, import surges: they've been protected for five years. No variation in new economic date b/c they've been insulated
					\item What's the economic test? There really isn't one. ``Would there be injury if we removed the duty?''
					\item Politics could be that theory (my theory from above)
						\begin{itemize}
							\item Q: Does hiring of lawyers for AD procedure get caught up in LDA data?
						\end{itemize}
				\end{itemize}
		\end{itemize}
\end{itemize}
